---
title: "Team Assignment2 for DA1"
author: "liyue"
date: "10/20/2019"
output: pdf_document
---



```{r}
library(readxl)
da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
View(da1_asgn)
```

1.Discuss the data collection, difficulties, problems. How you picked product 2. How did you decide on store features to record and how did you code it? (2-3 paragraphs) [1p]



2.Present descriptive statistics of prices. You may do it with one or two tables as you see fit [1p]

```{r}
summary(da1_asgn$Price_of_Coca_Cola)
sd(na.omit(da1_asgn$Price_of_Coca_Cola))


```


3.Show two descriptive graphs of price distributions of your products in the whole data (ie two districts merged). [0.5p]

```{r}
library(ggplot2)
da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
Graph_2<- ggplot(da1_asgn, aes(Price_of_Orbit))
Graph_2+ geom_histogram(position = 'identity', alpha = 0.7, binwidth = 10, aes(y = ..density..,fill = factor(InnerCity_or_NOT)))+
    stat_density(geom = 'line', position = 'identity', aes(colour = factor(InnerCity_or_NOT)))


```

```{r}
library(ggplot2)
da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
Graph_3<- ggplot(da1_asgn, aes(Price_of_Orbit))
Graph_3+ geom_histogram(position = 'identity', alpha = 0.5, binwidth = 10, aes(fill = factor(InnerCity_or_NOT)))+
    stat_count(geom = 'point', position = 'identity', aes(colour = factor(InnerCity_or_NOT)))
```

4.Show two descriptive graphs of price distributions of Coca Cola in the two districts merged [0.5p]
```{r}
library(ggplot2)
da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
Graph_4<- ggplot(da1_asgn, aes(Price_of_Coca_Cola))
Graph_4+ geom_histogram(position = 'identity', alpha = 0.5, binwidth = 20, aes(y = ..density..,fill = factor(InnerCity_or_NOT)))+
    stat_density(geom = 'line', position = 'identity', aes(colour = factor(InnerCity_or_NOT)))
```


```{r}
library(ggplot2)
da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
Graph_5<- ggplot(da1_asgn, aes(Price_of_Coca_Cola))
Graph_5+ geom_histogram(position = 'identity', alpha = 0.5, binwidth = 20, aes(fill = factor(InnerCity_or_NOT)))+
    stat_count(geom = 'point', position = 'identity', aes(colour = factor(InnerCity_or_NOT)))
  
```

5.Test if the price of Coca Cola is the same in the two districts. [1p]


```{r}
library(ggplot2)
library(tidyverse)
da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
Test_price<- da1_asgn%>%
  group_by(InnerCity_or_NOT)%>%
  summarise('ave_price2' = mean(Price_of_Coca_Cola,na.rm = TRUE))%>%
  ggplot(mapping = aes(x= InnerCity_or_NOT, y=ave_price2,fill=InnerCity_or_NOT))+
  scale_x_continuous(breaks = c(0:1),labels = c('Suburbs','Innercity'))+
  scale_colour_hue(breaks = c(0:1),labels = c('Suburbs','Innercity'))+
  geom_bar(position="dodge",stat="identity")+
  labs(x = 'Innercity or Not', y = 'Average Pice of Coca Cola')+
  theme_bw()

innercity=da1_asgn[da1_asgn$InnerCity_or_NOT==1,]
outercity=da1_asgn[da1_asgn$InnerCity_or_NOT==0,]
  
t.test(innercity$Price_of_Coca_Cola,outercity$Price_of_Coca_Cola)
  

```

```{r}

da1_asgn<- read_excel("~/Desktop/DA1/da1-asgn-Saroyan_Kiss_Li.xlsx")
da1_asgn

da1_asgn$InnerCity_or_NOT  <- as.factor(da1_asgn$InnerCity_or_NOT)

Graph_0<- ggplot(da1_asgn, aes(x= InnerCity_or_NOT, y= Price_of_Coca_Cola))
Graph_0+ geom_boxplot()
```

6.Summarize your findings regarding price distributions [1p]







7.Now pick any feature of stores and create a binary variable. Pool your data across districts. Compare prices by this new variable and discuss. [1p]


```{r}
library(dplyr)
da1_asgn$big_store <- ifelse(da1_asgn$No_of_cashier>1,T,F)
table(da1_asgn$big_store)


library(ggplot2)
Graph_6<- ggplot(da1_asgn, aes(Price_of_Coca_Cola))
Graph_6+ geom_histogram(position = 'identity', alpha = 0.5, binwidth = 20, aes(fill = factor(big_store)))



library(ggplot2)
Graph_7<- ggplot(da1_asgn, aes(Price_of_Orbit))
Graph_7+ geom_histogram(position = 'identity', alpha = 0.5, binwidth = 20, aes(fill = factor(big_store)))
```



